Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-20 paper/v1.0/sections/1_introduction.tex
Add introduction final part

>>>>

The paper is organized as follows. In Sec.  \ref{sec_schrodinger_problem}, we introduce our dressed quantum Hall system and the exact wave function solutions for the given configuration. Sec. \ref{sec_floquet_theory}, provides the Floquet theory interpretation of these wave functions.
We introduce Floquet Fermi golden rule for quantum Hall system in Sec. \ref{sec_inverse_scattering_time}, and we use it in Sec. \ref{sec_floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
The derived theoritical model is further analyzed numerically using empherical system parameters and compared with previous studies in Sec. \ref{sec_manipulate_conductivity}, followed by concluding remarks in Sec. \ref{sec_conclusions}.
